The Exoplanet Orbit Database 2, 2014 updates

### 2014-03-11 draft/ms.tex
Section 2 intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}
Make sure to cite \cite{Wright2013} for the definition of orbital elements.

@@

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
here that though we focus on EOD in this Section, the fields apply to
all planets on exoplanets.org.

%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Updates on the EOD}\label{sec:update}

The scope of the EOD has not been changed much but there was a major change in the category of host star. Previously, we only included exoplanets orbiting the `normal stars', but exoplanets orbiting neutron stars are also in our database. Furthermore, we only had exoplanets that were discovered by RV and transit but as more exoplanets are discovered by various methods such as microlensing and imaging, we have included those exoplanets as well into our database.

We still require the ``planets" to be smaller than 24 \mjup\ and the robust detection, which although is not strictly quantitative.

The purpose of the EOD has not changed; we aim to provide the readers with comprehensive database for exoplanets that are discovered up-to-date. However, we just do not put all the announced exoplanets as we are not trying to do ``an encyclopedic presentation of every claimed detection of an exoplanet" as mentioned in \cite{Wright2011}.

@@

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}} Make a note
here that though we focus on EOD in this Section, the fields apply to
all planets on exoplanets.org.
Make sure to cite \cite{Wright2013} for the definition of orbital elements. 
%------------------------------------------------------------------------------
\subsection{Discovery and References}\label{sec:disc}
